Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/experiments.tex
edits

We evaluated HSLDA along with three closely related models against 
these two datasets. The comparison models included sLDA with independent 
regressors (hierarchical constraints on labels ignored), HSLDA fit by first
performing LDA then fitting tree-conditional regressions. These models were
chosen to  highlight several aspects of HSLDA including performance in the
absence  of hierarchical constraints, the effect of the combined inference, and
regression performance attributable solely to the hierarchical constraints.

@@

For all of these models, particular attention was payed to the settings of the
prior parameters for the regression coefficients. These parameters implement an
important form of regularization in HSLDA. In the setting where there are no negative
labels, a Gaussian prior over the regression parameters with a negative mean implements
a prior belief that missing labels are likely to be negative. We evaluated model performance 
for all three models with a range of values for $\mu$, the mean prior parameter for regression coefficients
($\mu\in\left\{ -3,-2.8,-2.6,\ldots,1\right\}$).

@@

@@

We evaluated our model, HSLDA, against the comparison models with a focus
on predictive performance on held-out data. Prediction performance was measured with
standard metrics - sensitiviy (true positive rate) and 
1-specificity (false positive rate).

To evaluate the performance of these models, we established a gold standard for comparison.
For each dataset, a held out set of 1000 documents and labels were
reserved for evaluation and predictive performance was evaluated against a standard derived
from the observed labeling. To make the comparison as fair as possible, 
ancestors of observed nodes were ignored, observed nodes 
were considered positive and descendents of observed nodes were considered to be negative. This method of 
defining positive and negative labels was chosen to be as fair as possible to all models
being compared.  In particular, since the sLDA model does not enforce the hierarchical
constraints, its performance was found to be so poor on joint prediction that it was not included.
The models can be compared on a more equal footing by considering only on the observed labels
as being positive despite the fact that ancestors must also be positive. The gold standard 
defined in this way will likely inflate the number of
false positives because the labels applied to any particular document are usually not as complete as they could be. 
ICD-9 codes lack sensitivity and their use as a
gold standard could lead to correctly positive predictions being labeled as false positives\citep{Birmetal2005}.
However, given that the label space is often large (as in our examples) it is a moderate assumption that
erroneous false positives should not skew results significantly.

@@

\begin{figure}%[htbp]
\begin{center}
%\subfloat[][\label{fig:1a}]{\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\subfigure[][]{\label{fig:1a}\includegraphics[width=.49\textwidth]{figs/clin_pred_varying_mu}}
%\subfloat[][\label{fig:1c}]{\includegraphics[width=.49\textwidth]{figs/sens_comparison_leafs}}
\subfigure[][]{\label{fig:1b}\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\subfigure[][]{\label{fig:clinical_roc}\includegraphics[scale=0.4]{figs/ROC_comparison_leafs}}
\caption{ROC curves for out-of-sample ICD-9 code prediction from patient free-text discharge records 
(\subref{fig:1a},\subref{fig:clinical_roc}). ROC curve for out-of-sample Amazon product category predictions from 
product free-text descriptions \subref{fig:1b}. Figures \subref{fig:1a} and \subref{fig:1b} are a function 
of the prior means of the regression parameters. Figure \subref{fig:clinical_roc} is a function of auxiliary variable threshold. In all figures, solid is 
HSLDA, dashed are independent regressors + sLDA (hierarchical 
constraints on labels ignored), and dotted is HSLDA fit by running LDA first then running 
tree-conditional regressions.}
\label{fig:main_results}
\end{center}
\end{figure}

>>>>

We evaluated HSLDA along with two closely related models against
the two datasets. The comparison models included sLDA with independent
regressors (hierarchical constraints on labels ignored), HSLDA fit by first
performing LDA then fitting tree-conditional regressions. These models were
chosen to  highlight several aspects of HSLDA including performance in the
absence  of hierarchical constraints, the effect of the combined inference, and
regression performance attributable solely to the hierarchical constraints.

@@

For all three models, particular attention was given to the settings of the 
prior parameters for the regression coefficients. These parameters implement an
important form of regularization in HSLDA. In the setting where there are no
negative labels, a Gaussian prior over the regression parameters with a
negative mean implements a prior belief that missing labels are likely to be
negative. Thus, we evaluated model performance for all three models with a
range of values for $\mu$, the mean prior parameter for regression coefficients 
($\mu\in\left\{ -3,-2.8,-2.6,\ldots,1\right\}$).

@@

\begin{figure}[h]
\begin{center}
%\subfloat[][\label{fig:1a}]{\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\subfigure[][]{\label{fig:1a}\includegraphics[width=.49\textwidth]{figs/clin_pred_varying_mu}}
%\subfloat[][\label{fig:1c}]{\includegraphics[width=.49\textwidth]{figs/sens_comparison_leafs}}
\subfigure[][]{\label{fig:1b}\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\subfigure[][]{\label{fig:clinical_roc}\includegraphics[scale=0.4]{figs/ROC_comparison_leafs}}
\caption{ROC curves for out-of-sample ICD-9 code prediction from patient free-text discharge records 
(\subref{fig:1a},\subref{fig:clinical_roc}). ROC curve for out-of-sample Amazon product category predictions from 
product free-text descriptions \subref{fig:1b}. Figures \subref{fig:1a} and \subref{fig:1b} are a function 
of the prior means of the regression parameters. Figure \subref{fig:clinical_roc} is a function of auxiliary variable threshold. In all figures, solid is 
HSLDA, dashed are independent regressors + sLDA (hierarchical 
constraints on labels ignored), and dotted is HSLDA fit by running LDA first then running 
tree-conditional regressions.}
\label{fig:main_results}
\end{center}
\end{figure}

@@

We evaluated our model, HSLDA, against the comparison models with a focus on
predictive performance on held-out data. Prediction performance was measured
with standard metrics -- sensitiviy (true positive rate) and 1-specificity
(false positive rate).

The gold standard for comparison was derived from the testing set in each
dataset. To make the comparison as fair as possible among models, ancestors of
observed 
nodes in the label hierarchy were ignored, observed nodes were considered
positive and descendents of observed nodes were considered to be negative. In
particular, since the sLDA model does not enforce the hierarchical constraints,
its performance was found to be so poor on joint prediction that it was not
included. 
The models can be compared on a more equal footing by considering only on the observed labels
as being positive despite the fact that ancestors must also be positive. The gold standard 
defined in this way will likely inflate the number of
false positives because the labels applied to any particular document are usually not as complete as they could be. 
ICD-9 codes lack sensitivity and their use as a
gold standard could lead to correctly positive predictions being labeled as false positives\citep{Birmetal2005}.
However, given that the label space is often large (as in our examples) it is a moderate assumption that
erroneous false positives should not skew results significantly.

@@
